Template for preparing your Brief Report submission to PNAS using Overleaf

### 2023-11-22 PNAS/index.Rnw
Add FDR/FWER paper
Tweaking formatting of first page, add acknowledgements.
Tweak first page, add acknowledgements.

\firstpage[4]{6}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

\dropcap{M}ultiple comparisons are a persistent problem for statistical methods and for science. In forensic statistics, researchers have been focusing on the necessity of building up research databases which can be used to develop objective algorithms for evidence comparisons and explore closest non-matches \citep{pcast}. While these databases (and open data) are critically important in forensics, we also need to be careful about how our methods are affected by the multiple comparison problem.

@@

\section*{Wire Cut Forensics}

@@

\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}

>>>>

\firstpage[8]{7}
% Use \firstpage to indicate which paragraph and line will start the second page and subsequent formatting. In this example, there are a total of 11 paragraphs on the first page, counting the first level heading as a paragraph. The value {12} represents the number of the paragraph starting the second page. If a paragraph runs over onto the second page, include a bracket with the paragraph line number starting the second page, followed by the paragraph number in curly brackets, e.g. "\firstpage[4]{11}".

@@

\dropcap{M}ultiple comparisons are a persistent problem when developing statistical methods for scientific problems \citep{benjaminiControllingFalseDiscovery1995}. In forensic statistics, researchers have been focusing on the necessity of building up research databases which can be used to develop objective algorithms for evidence comparisons and explore closest non-matches \citep{pcast}. While these databases (and open data) are critically important in forensics, we also need to be careful about how our methods are affected by the multiple comparison problem.

@@

\section*{Examination Process}

@@

\acknow{This work was funded (or partially funded) by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreements 70NANB15H176 and 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.}
